Ethnicity sensitive author disambiguation of semi-labeled corpora of scientific articles

### 2015-08-25 paper/paper.tex
save

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/workflow}
\caption{General pipeline for author disambiguation: (a)
signatures are \textit{blocked} to reduce computational complexity, (b) a linkage
function is built with supervised learning, (c) signatures within the same block
are grouped using agglomerative clustering.}
\label{fig:workflow}
\end{figure}

@@

\glnote{Add a few examples of transformed pairs?}

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/workflow}
\caption{Pipeline for author disambiguation: (a)
signatures are \textit{blocked} to reduce computational complexity, (b) a linkage
function is built with supervised learning, (c) independently within each block, signatures
are grouped using agglomerative clustering.}
\label{fig:workflow}
\end{figure}

@@

%\glnote{Add a few examples of transformed pairs?}
